Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-09-06 doc/manuscript/manuscript.Rmd
5 -> five

Table: (\#tab:region-aggressiveness) Mean aggressiveness ratings for the Regions with greater than 5 samples; groupings according to 95% family-wise confidence interval.

>>>>

Table: (\#tab:region-aggressiveness) Mean aggressiveness ratings for Regions with more than five samples; groupings according to 95% family-wise confidence interval.
